RAS2012: Competition Entry

### 2012-07-14 ras2012-paper/src/main/latex/paper/paper.tex
Newly benchmarked results.

Running the algorithm described above 20 times over each data set, we have compiled a set of results, see Table \ref{table:result}. All these were reached within 3 minutes in a single-threaded run, using Intel i7 Q820 processor running Fedora 17 and 2 GB of heap space inside Java 7 runtime environment.

@@

For statistics of the resolved systems, see tables \ref{table:TOY-808.tex}, \ref{table:RDS1-996.tex}, \ref{table:RDS2-7597.tex} and \ref{table:RDS3-11023.tex} respectively.

@@

\include{TOY-808}
\include{RDS1-996}
\include{RDS2-7597}
\include{RDS3-11023}

>>>>

Running the algorithm described above 50 times over each data set, we have compiled a set of results, see Table \ref{table:result}. All these were reached within 3 minutes in a single-threaded run, using Intel i7 Q820 processor running Fedora 17 and 2 GB of heap space inside Java 7 runtime environment.

@@

For statistics of the resolved systems, see tables \ref{table:RASDATASET1}, \ref{table:RASDATASET2} and \ref{table:RASDATASET3} respectively.

@@

\include{RDS1-1199}
\include{RDS2-7955}
\include{RDS3-11306}
